Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-19 paper.tex
nothing

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement, which are presented in Section \ref{sec:probForm}. The proposed algorithm (Section~\ref{sec:propSol}) relies on indicators that can be easily computed in low-power smart cameras, such as the average image intensity or frame difference (to detect camera displacement), and the average gradient norm (to detect blurring), and detects tampering as frames yielding outliers. In particular, we show that separately monitoring indicators over different regions of the image can substantially improve the displacement-detection performance. Remarkably, image regions can be preliminarily defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Thus, our solution represents a prompt trigger that can be possibly combined with other sequential monitoring techniques. Experiments in Section \ref{sec:experiments} show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.
\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 3-rd frame, created using gaussian filtering; \textbf{(c)} displacement event on 3-rd frame, created moving the crop of the original image from the center.}
\label{fig:sequences}
\end{figure}

@@

\begin{figure}[t]
\centering
\subfigure[]{\label{fig:ROCdisplacement}\includegraphics[width=0.45\linewidth]{Immagini/ROCdisplacement}}
\subfigure[]{\label{fig:ROCdefocus} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus}}
\caption{\textbf{(a)} ROC curve for displacement detection.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} (Luma-Region) is $99.94\%$, the AUC of Luma-Total is $99.89\%$ the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.96\%$) outperforms the Gradient-Regions (AUC $98.95\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement, which are presented in Section \ref{sec:probForm}. The proposed algorithm (Section~\ref{sec:propSol}) relies on indicators that can be easily computed in low-power smart cameras, such as the average image intensity or frame difference (to detect camera displacement), and the average gradient norm (to detect blurring), and detects tampering as frames yielding outliers. In particular, we show that separately monitoring indicators over different regions of the image can substantially improve the displacement-detection performance. Remarkably, image regions can be preliminarily defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Thus, our solution represents a prompt trigger that can be possibly combined with other sequential monitoring techniques. Experiments in Section \ref{sec:experiments} show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.
\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} defocus event on 3-rd frame, created using gaussian filtering; \textbf{(b)} displacement event on 3-rd frame, created moving the crop of the original image from the center.}
\label{fig:sequences}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curve for displacement detection.
	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
	The AUC corresponding to Algorithm~\ref{alg:DISPL} (Luma-Region) is $99.94\%$, the AUC of Luma-Total is $99.89\%$ the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
	\textbf{(b)} ROC curve for blurring detection.
	In this case, the Gradient-Total (AUC $99.96\%$) outperforms the Gradient-Regions (AUC $98.95\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
